---
title: "lecture 4 example"
author: "Sarah Lam"
date: "2023-02-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Try this - make a random sample of fertilizer application, 10 values with mean of 5 and standard deviation of 0.5
(user rnorm function in R to do this)
```{r}
fert_app <- rnorm(n = 10, mean = 5, sd = 0.5)
```

Function to computed crop yield
Lets imagine that annual yield of a crop can be estimated follows:
yield=1.8∗fertilizer2−0.5∗fertilizer+0.1∗TP
and TP is mean precipitation in cm

Task 1: Use a for loop to compute the total yield after 10 years
- fertilizer is normally distributed with mean of 5 and standard deviation of 0.5
- TP is 20cm
```{r}
TP = 20

total_yield = for (yr in 1:10) {
 total_yield = 
}

```

Task 2: create a function to that takes as input a single value for annual fertilizer and annual total precipitation and returns yield

Task 3: modify your function so that it returns total yield if the user inputs a vector of fertilizer and a vector of precipitation

Check that function returns the same result as your original for loop

Add some error checking and test
